---
title: "With  shinyStorePlus v0.8, transfer browser link parameters to shiny inputs or outputs"
author: "Obinna N. Obianom"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{With  shinyStorePlus v0.8, transfer browser link parameters to shiny inputs or outputs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

__Imagine that your browser link looks something like this: http://127.0.0.1:6316/?data=pressure&name=obinna&num=50&outt=wowowow __

What if you'd like the transfer the value of __data__ and __name__ and __num__ to a shiny input, and the value of __outt__ to a shiny output. That can be accomplished using shinyStorePlus' latest version. 

Here is how you do it ...

<style>body{max-width:unset!important;}pre.sourceCode{background-color:#d8d800!important;}code.sourceCode{background-color:#d8d800!important;color:fff!important;}</style>

## Step 1: Start with an already working application

Below is the code for an application to which we will integrate the shinyStorePlus package

```{r eval=FALSE,echo=TRUE}

# library
library(shiny)

if(interactive()) {
ui <- fluidPage(
  # Application title
  titlePanel("Transfer browser link parameters to shiny input"),

  # Sidebar with a slider input for number of bins
  selectInput(
    inputId = "datasetbin",
    label = "Choose an option",
    choices = c("rock", "pressure", "cars")
  ),
  textInput(
    inputId = "cd323",
    label = "Choose a name",
    value = "No name"
  ),

  numericInput(
    inputId = "number1",
    label = "Choose a number",
    value = 10
  ),
  
  htmlOutput("outputnum")
)

server <- function(input,output,session) {
}

shinyApp(ui = ui, server = server)
}

```


## Step 2: Install and attach the <code>shinyStorePlus 0.8</code> R package

The shinyStorePlus package is available on CRAN and can be installed as shown below

`install.packages(shinyStorePlus)`

Attach library 

`library(shinyStorePlus)`

Now, the code you have should look like this ...


```{r eval=FALSE,echo=TRUE}

# library
library(shiny)
library(shinyStorePlus)

if(interactive()) {
ui <- fluidPage(
  # Application title
  titlePanel("Transfer browser link parameters to shiny input"),

  # Sidebar with a slider input for number of bins
  selectInput(
    inputId = "datasetbin",
    label = "Choose an option",
    choices = c("rock", "pressure", "cars")
  ),
  textInput(
    inputId = "cd323",
    label = "Choose a name",
    value = "No name"
  ),

  numericInput(
    inputId = "number1",
    label = "Choose a number",
    value = 10
  ),
  
  htmlOutput("outputnum")
)

server <- function(input,output,session) {
}

shinyApp(ui = ui, server = server)
}

```


## Step 3: Initialize by including the scripts required for processing the stores

You must now initialize for the package to work. Its as simple as inserting the function below within the <code>fluidPage()</code>

`initStore()`

Now, the code you have should look like this ...


```{r eval=FALSE,echo=TRUE}

# library
library(shiny)
library(shinyStorePlus)

if(interactive()) {
ui <- fluidPage(
  
  #Initialize shinyStorePlus
  initStore(),
  
  # Application title
  titlePanel("Transfer browser link parameters to shiny input"),

  # Sidebar with a slider input for number of bins
  selectInput(
    inputId = "datasetbin",
    label = "Choose an option",
    choices = c("rock", "pressure", "cars")
  ),
  textInput(
    inputId = "cd323",
    label = "Choose a name",
    value = "No name"
  ),

  numericInput(
    inputId = "number1",
    label = "Choose a number",
    value = 10
  ),
  
  htmlOutput("outputnum")
)

server <- function(input,output,session) {
}

shinyApp(ui = ui, server = server)
}

```



## Step 4: Setup the matching of parameters to input values

Match the Shiny input IDs to paramters in the link.

Now, the code you have should look like this ...


```{r eval=FALSE,echo=TRUE}

# library
library(shiny)
library(shinyStorePlus)

if(interactive()) {
ui <- fluidPage(
  
  #Initialize shinyStorePlus
  initStore(),
  
  # Application title
  titlePanel("Transfer browser link parameters to shiny input"),

  # Sidebar with a slider input for number of bins
  selectInput(
    inputId = "datasetbin",
    label = "Choose an option",
    choices = c("rock", "pressure", "cars")
  ),
  textInput(
    inputId = "cd323",
    label = "Choose a name",
    value = "No name"
  ),

  numericInput(
    inputId = "number1",
    label = "Choose a number",
    value = 10
  ),
  
  htmlOutput("outputnum")
)

server <- function(input,output,session) {
  # for the inputs
  link2input(
    #example: shiny element ID = link parameter
    cd323 = "name",
    datasetbin = "data",
    number1 = "num"
    )
  #for the outputs
  link2input(
    outputnum = "outt",
    inputtype = "output"
  )
  
}

shinyApp(ui = ui, server = server)
}

```

## Step 5: Run the final code and include the parameters in the browser link

Paste the final R code into your console and run. When the Shiny link launches, it may look something like this " __http://127.0.0.1:6316 __ "

Now, you must include the parameters in the browser link to see the magic happen. So now, you can transform that link into  " __http://127.0.0.1:6316/?data=pressure&name=obinna&num=50&outt=wowowow __ "

That will work!

  
## Official links

Documentation: https://shinystoreplus.obi.obianom.com
Code and report issues: https://github.com/oobianom/shinyStorePlus/issues

